\section{Research Design}

Knowing the context of the research problem,
this chapter will contain information on how the research will be done.
There are seven steps that will be taken,
each being explained briefly.

\subsection{Understanding the Problem}
Begin with a detailed description of the problem
- the need to interpret, process, and confirm hand-written forms.
Discuss why this is a challenge and the implications of not addressing it.

\subsection{Role of Cloud Computing}
Discuss how cloud computing can potentially address this problem.
Highlight the specific capabilities of cloud computing that make it suitable for this task.

\subsection{Analyzing the Building Blocks}
Analyze the selected Azure building blocks in the context of the problem.
Discuss how each building block can contribute to the solution.
Selecting those most suited for the problem.

\subsection{Software Quality}
Discuss the importance of software quality in the context of this problem.
Refer to the ISO 25010 standard, which defines a quality model for software products.
Discuss how the various characteristics defined in the standard
(such as functionality, reliability, usability, efficiency, maintainability, and portability \cite{ISO25010})
apply to the problem and the proposed solution.

Diagrams will be used to provide insights in the characteristics defined in the standard.
Class Diagram and Use Case Diagrams can be relevant in other part of the projects.
Howevers, since the research will combine different building blocks from Azure,
Sequence Diagrams for communication between components, Activity Diagrams for simplified
feature flows and Component Diagrams for the structuring of the building blocks,
will be made in this regard.

\subsection{Potential Challenges}
dentify potential challenges in using cloud computing for this task.
This could include technical challenges, data security concerns, etc.

\subsection{Proposed Approach}
Based on the analysis, propose an approach to address the problem using Azure`s building blocks.
This approach should be tentative and open to changes as the research progresses.

\subsection{Prototyping}
Discuss the importance of creating a prototype to test the proposed solution.
Outline the steps involved in developing the prototype and how it will be used to validate the findings of the research.

\subsection{Evaluation}
Combine everything learned up to this point and make a final recommendation
on the use of cloud computing from the perspective of the proposed approach. 